Spatial Analysis

### 2021-11-29 Scripts/spatial_analisis.Rmd
Fixed ME NH lat issue

state_lat <- historic_spp %>%
  group_by(state) %>% 
  summarise(
    order = mean(lat)
  ) %>% 
  filter(!is.na(state)) %>% 
  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
  ) %>% 
  arrange(desc(order)) %>% 
  mutate(lat = order,
    # order = letters[1:11],
    order = c("b","a",letters[3:11]),)

>>>>

state_lat <- historic_spp %>%
  group_by(state) %>% 
  summarise(
    order = mean(lat)
  ) %>% 
  filter(!is.na(state)) %>% 
  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA"),
         order = ifelse(abrev == "ME", order+1,order)
  ) %>% 
  arrange(desc(order))
